---
title: "Data-Processing_Float-Trap-Data"
author: "Jonny Behrens"
date: "`r Sys.Date()`"
output: html_document
---

# Overview

Floating emergence traps were deployed (~9 per site) in Ellerbe Creek and 
New Hope Creek in 2021 and 2022. This code cleans field data for analysis.

# Section 1: Set Up Environment

```{r setup, echo = FALSE, warning= FALSE, message=FALSE, results='hide'}
# Set working directory. Place the .here file in the desired working directory
knitr::opts_knit$set(root.dir = here::here())

# Some knit settings 
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# Clear environment
rm(list = ls())

# Load libraries
library(pacman)
p_load(openxlsx,knitr,DT, tidyverse)
```

# Section 2: Download and Clean Data

## Meta data

```{r}
trap_count<-read.csv("data_meta/meta_float-trap-count.csv") %>% 
  mutate(Collect.Date = as.Date(Collect.Date, tryFormats = c("%m/%d/%Y")))

float_meta_data<-read.csv("data_meta/meta_float-trap-deployment-schedule.csv") %>% 
  mutate(Collect.Date = as.Date(Date_Collected, tryFormats = "%m/%d/%Y")) %>% 
  dplyr::select(Collect.Date, Days_Deployed) %>% 
  filter(!is.na(Collect.Date))
```

Standard error is calculated for each Order of taxa at a given site and date.
This will subsequently be propagated (e.g., to families within order).

```{r}
families<-data.frame(EPTDO = c("E", "P", "T", "D", "O", "OR", "SO", "L", "R"), 
                     Order = c("ephemeroptera", "plecoptera", "trichoptera", 
                               "diptera", "other", "odonata",
                               "other", "other", "other"))
```

```{r}
std.error <- function(x) sd(x)/sqrt(length(x))

Emergence_FLOAT_Trap_Datav2 <- read.xlsx("data_raw/Bio/9-28-23_EC_Emergence_FLOAT_Trap_Datav2.xlsx") %>% 
  mutate(Collect.Date = as.Date(Collect.Date, origin = "1899-12-30"))

Emergence_Stats_EPTDO<- Emergence_FLOAT_Trap_Datav2 %>% 
  summarize(Total_mass_EPTDO = sum(Sample.Mass, na.rm = T),
            .by = c("Collect.Date", "Site", "EPTDO", "Float")) %>% 
  mutate(mean_EPTDO = mean(Total_mass_EPTDO),
         SE_EPTDO = std.error(Total_mass_EPTDO),
         n_EPTDO = n(),
         totalmass_EPTDO = sum(Total_mass_EPTDO), 
         SE_totalmass_EPTDO = n_EPTDO*SE_EPTDO,
         SE_percent_of_mass = round(SE_EPTDO/mean_EPTDO, 4), 
         .by = c("Collect.Date", "Site", "EPTDO")) %>% 
  mutate(SE_bigger_mean = if_else(SE_EPTDO >= mean_EPTDO, "Y", "N")) %>% 
  # we will conservatively call SE 100% of mean when there is only one observation
  mutate(SE_percent_of_mass = if_else(is.na(SE_percent_of_mass), 1, SE_percent_of_mass)) %>% 
  full_join(families)

results <- Emergence_Stats_EPTDO %>%
  filter(n_EPTDO > 2) %>% 
  mutate(t_test = list(t.test(Total_mass_EPTDO)),
         .by = c("Collect.Date", "Site", "EPTDO")) %>% 
  mutate(conf_int = map(t_test, ~ .$conf.int)) %>% 
  filter(map_lgl(conf_int, ~ !is.null(.x))) %>% 
  mutate(column1 = map_chr(conf_int, 1),
         column2 = map_chr(conf_int, 2)) %>% 
  select(-t_test, -conf_int)
```

## Biota data

Step 1: AFDM.mg is the total emergent biomass (AFDM) across all deployed traps
on a given date at a given site. For some sites, there were fewer than 9 traps 
(e.g., due to loss of a trap). Thus, divide first by n_traps*Day_Deployed to 
get a daily rate for each trap. Next, multiply by 3 since a traps is 1/3 of a m3.
The end results is a mg AFDM / m2 day rate.

Step 2: Calculate total mass emerging from a site on a given day by taxa, site, date.

Step 3: Same as step 2, but for each date (not taxa).

```{r}
Float_data_raw<-read.csv("data_raw/raw_Float_Biomass_3-6-24.csv") %>% 
  mutate(Collect.Date = as.Date(Collect.Date, tryFormats = c("%m/%d/%Y"))) %>% 
  full_join(trap_count) %>% 
  mutate(across(Order:Order_Family, tolower)) %>% 
  full_join(float_meta_data) %>% 
  left_join(select(Emergence_Stats_EPTDO, 
                   c(Collect.Date, Site, Order, SE_percent_of_mass)))

Float_data<-Float_data_raw %>% 
  # Step 1
  mutate(E_AFDM_mgperm2 = (AFDM.mg/(n_traps*Days_Deployed))*3,
         E_AFDM_mgperm2_SE = E_AFDM_mgperm2*SE_percent_of_mass) %>% 
  # Step 2
  mutate(FamilySite_E_AFDM_mgperm2 = sum(E_AFDM_mgperm2),
         FamilySite_E_AFDM_mgperm2_SE = sum(E_AFDM_mgperm2_SE),
         .by = c("Collect.Date", "Site", "Family")) %>% 
  # Step 3
  mutate(Site_E_AFDM_mgperm2 = sum(E_AFDM_mgperm2), 
         Site_E_AFDM_mgperm2_SE = sum(E_AFDM_mgperm2_SE),
         .by = c("Collect.Date", "Site")) %>% 
  # add season
  mutate(Month = month(Collect.Date),
         Season = if_else(Month %in% c(12,1,2), "Winter",
                  if_else(Month %in% c(3,4,5), "Spring",
                  if_else(Month %in% c(6,7,8), "Summer",
                  if_else(Month %in% c(9,10,11), "Fall", NA_character_)))),
                  .after=Month) %>% 
  # fix site names
  mutate(Site = case_when(Site == "NHC" ~ "forested",
                          Site == "ECGS" ~ "wastewater dominated",
                          Site == "ECNG" ~ "stormwater dominated"))

Taxa<-distinct(Float_data, Order, Family)
```

## Annual Flux - Imputed

```{r}
# Set the start and end dates
start_date <- as.Date("2021-04-15")
end_date <- as.Date("2022-04-16")
```

```{r}
# Create datasets to fill gaps (next section)
days <- seq(start_date, end_date, by = "1 day")

float_taxa_sampledates<-expand.grid(Site = unique(Float_data$Site),
                                    Order_Family = unique(Float_data$Order_Family),
                                    Collect.Date = unique(Float_data$Collect.Date)) %>% 
  filter(!is.na(Collect.Date)) %>% 
  mutate(Order = str_extract(Order_Family, "[:alpha:]+"))
  
float_time_series<-expand.grid(Site = unique(Float_data$Site),
                               Order_Family = unique(Float_data$Order_Family),
                               Collect.Date = days)  %>% 
  mutate(Order = str_extract(Order_Family, "[:alpha:]+"))
```

```{r}
tree_data_emerge<-Float_data %>%
  filter(!is.na(Site)) %>% 
  distinct(Site, Order, Order_Family, Collect.Date, 
           FamilySite_E_AFDM_mgperm2,FamilySite_E_AFDM_mgperm2_SE) %>% 
  # Fill in zeros for each sampling dates
  full_join(float_taxa_sampledates) %>% 
  mutate(FamilySite_E_AFDM_mgperm2 = if_else(is.na(FamilySite_E_AFDM_mgperm2), 
                                                0, FamilySite_E_AFDM_mgperm2),
         FamilySite_E_AFDM_mgperm2_SE = if_else(is.na(FamilySite_E_AFDM_mgperm2_SE), 
                                                0, FamilySite_E_AFDM_mgperm2_SE)) %>% 
  # Add empty rows for all missing days
  full_join(float_time_series) %>%
  # Impute to estimate annual flux
  arrange(Site, Order_Family, Collect.Date) %>% 
  group_by(Site, Order_Family) %>% 
  mutate(imputed_data = imputeTS::na_interpolation(FamilySite_E_AFDM_mgperm2, option = "linear"),
         imputed_data_SE = imputeTS::na_interpolation(FamilySite_E_AFDM_mgperm2_SE, option = "linear")) %>% 
  ungroup()
```

# Section 3: Save Data

```{r echo = T}
write.csv(Float_data, "data_processed/Emergence_Float_DryAquaticInsects_8-13-24.csv")
write.csv(tree_data_emerge, "data_processed/Tree-Data-Emergence_8-13-24.csv")
```
